We are going to write a book about a guy who is hired as the new directory of security for a manufacturing company. He is going to deploy a security program at the company.
The board of directors are concerned that a cyber incident will shutdown production.
The director of security is going to follow NIST Cybersecurity Framework.

For each character listed, give a name and some additional back story.
Intertwine the threads into chapters and give a chapter summary from the threads.
Summarize the chapters so that each thread is represented.
Create a name for the company.

Main thread: John Renyolds, the new director of cyber security.
Presents NIST Cybersecurity Framework to the board.
Change corporate culture with cyber security awareness training
Start log management
Vulnerability management
Asset management
Gameify between operators and SOC on who will report/track vulnerabilities faster. Result: better/more IT documentation.
Metrics
Standards to support
Password manager
Phishing response
We report phish because our colleague doesn’t know where his bath towel
The answer to the question of “Are we being phished?” is yes! They rain down every minute of every day.
The better question is: “has anyone clicked a link?”
How do we know that?
Because people report phish, we know what the links are.
Now we go into our systems and find out who is clicking them.
Metrics
# of campaigns reported
# of recipients
# of reported
% of reported phish
Partition the network - from 3 vlans to purdue structure.
PIPEDA: real risk of significant harm
Just enough security
Develop Incident response plan
Established metrics surrounding:
Phishing
Vulnerability management
Company tries to hide breach. 
John must report to the privacy commissioner
Uses metrics collected from Phishing, vulnerability management to drive service strategy.
Improve cyber security awareness training by including cyber security items deployed over the last year, such as data classification.

CEO/Board:
Recent audit highlights unpreparedness for cyber event
Hires John Renyolds as a result.
Debates paying ransom

HR employee:
Search for jobs
Find one
Give notice
Depart on good terms
Note that the company does not have a standard process for terminations and that there is no notice given to the rest of the company of departures.

Affair between VP Marketing (CEO’s daughter) with COO.
VP marketing is married with 4 children
COO is married with 2 children
The affair is just a fling for stress relief
COO is terminated when the affair is used as leverage in ransomware
COO contemplates suicide in order to not have to go home to tell his wife that he has been fired for having an affair.

EA to Senior VP Finance
Husband recently killed in the line of duty.
Not sleeping well, consuming alcohol to cope.
Story opens with her return to work. Give a background story on how the CEO and founder calls the company Pre rather than PMS.
New cybersecurity requirements are daunting to her.
Falls for threat actors asking to confirm login id and password
This email was sent to 5 other employees, all who knew it was phish but choose to ignore it and not report it.
Her boss considers terminating her because of the breach.

Threat actors
Use former HR employee’s email to phish credentials from EA to Senior VP Marketing (and 5 other people)
Gain unpriviledged access to internet facing device, self hosted exchange server with OWA and only password authentication.
Exploit unpatched flaw from 2 years ago.
Use vulnerability to elevate privilege.
Get access to the bank accounts, transfer smaller sums out.
Gain access to email, exfiltrate, AI finds affair, also finds that there is a lot of cyber security action and confusion.
Get access to HR data, exfiltrate
Leverage HR data to ransom individual employees
Leverage affair to coerce IR team to pay ransom.
Taken down by international police force during ransomware negotiations.



